A Fundamental Measure Theory Functional for Hard-Sphere Contact Densities

### 2012-08-10 papers/contact/paper.tex
add MC data to outer-sphere plots Tested everything on node02.
new contact data and cleaned-up plots Tested everything on kipu.
select specific figures to include in paper Tested everything on kipu.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/walls-10}
  \caption{Density and contact densities at a wall with bulk filling
    fraction of 0.1.}
  \label{fig:walls-10}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/walls-30}
  \caption{Density and contact densities at a wall with bulk filling
    fraction of 0.3.}
  \label{fig:walls-30}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gnn-walls-10}
  \caption{Correlation multiplied twice by density with bulk filling
    fraction of 0.1.}
  \label{fig:gnn-walls-10}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gnn-walls-30}
  \caption{Correlation multiplied twice by density with bulk filling
    fraction of 0.3.}
  \label{fig:gnn-walls-30}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gnn-walls-40}
  \caption{Correlation multiplied twice by density with bulk filling
    fraction of 0.4.}
  \label{fig:gnn-walls-10}
\end{figure}

@@

@@

The next geometry we consider is a number of hard spheres confined
within a spherical cavity.  In
Figures~\ref{fig:sphere-8}-\ref{fig:sphere-16}, we show the densities
and contact densities for several cavity sizes \fixme{at a variety of
  filling fractions}.  We chose cavities that are large enough that
the center of the sphere is bulk-like, so that we can interpret the
behavior near the interface as behavior that should be typical of the
behavior of the hard sphere fluid near a concave surface.
\begin{center}
  \includegraphics[width=\columnwidth]{figs/outer-16-05}
\end{center}
\begin{center}
  \includegraphics[width=\columnwidth]{figs/outer-16-04}
\end{center}
\begin{center}
  \includegraphics[width=\columnwidth]{figs/outer-16-03}
\end{center}

@@

\begin{center}
  \includegraphics[width=\columnwidth]{figs/inner-4-30}
\end{center}
\begin{center}
  \includegraphics[width=\columnwidth]{figs/inner-4-40}
\end{center}
\begin{center}
  \includegraphics[width=\columnwidth]{figs/inner-8-30}
\end{center}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figs/gHS-vs-n}
\caption{A comparison of the various approximations to the contact
  density in the homogeneous limit.  As expected, they are all
  identical, and we won't include this plot in the paper (but it's
  here to verify that our code is working).}
\label{fig:gHS-vs-n}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figs/free-energy}
\caption{A comparison of the various approximations to the free energy
  in the homogeneous limit.  Note that the White Bear functional uses
  a modified form of the Carnahan equation of state.  As expected,
  these are all identical, and we won't include this plot in the paper
  (but it's here to verify that our code is working).}
\label{fig:free-energy}
\end{figure}

>>>>

\fixme{Consider eliminating $n_0$ and/or $n_A$ from the plots to make
  things cleaner.}

@@

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/walls-10}
  \caption{Density and contact densities at a wall with bulk filling
    fraction of 0.1.}
  \label{fig:walls-10}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-4-10}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.1.}
  \label{fig:inner-4-10}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-12-10}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.1.}
  \label{fig:inner-12-10}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/outer-12-01}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.1.}
  \label{fig:outer-10}
\end{figure}

@@

The next geometry we consider is a number of hard spheres confined
within a spherical cavity.  In
Figures~\ref{fig:sphere-8}-\ref{fig:sphere-16}, we show the densities
and contact densities for several cavity sizes \fixme{at a variety of
  filling fractions}.  We chose cavities that are large enough that
the center of the sphere is bulk-like, so that we can interpret the
behavior near the interface as behavior that should be typical of the
behavior of the hard sphere fluid near a concave surface.

@@

\section{Results}

\subsection{Test-particle result}

Here we discuss comparison of the correlation function calculated via
both Monte Carlo and the test-particle approach (see
Figures~\ref{fig:inner-4-10} and~\ref{fig:inner-4-40}).

\subsection{Low density}

Here we discuss the low-density results (filling fraction of 0.1),
which are shown in Figures~\ref{fig:walls-10}-\ref{fig:outer-10}.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-4-40}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.4.}
  \label{fig:inner-4-40}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-12-40}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.4.}
  \label{fig:inner-12-40}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/outer-16-04}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.4.}
  \label{fig:outer-40}
\end{figure}

\subsection{High density}

Here we discuss the high-density results (filling fraction of 0.4),
which are shown in Figures~\ref{fig:walls-40}-\ref{fig:outer-40}.

@@

%% \begin{figure}
%% \includegraphics[width=\columnwidth]{figs/gHS-vs-n}
%% \caption{A comparison of the various approximations to the contact
%%   density in the homogeneous limit.  As expected, they are all
%%   identical, and we won't include this plot in the paper (but it's
%%   here to verify that our code is working).}
%% \label{fig:gHS-vs-n}
%% \end{figure}

%% \begin{figure}
%% \includegraphics[width=\columnwidth]{figs/free-energy}
%% \caption{A comparison of the various approximations to the free energy
%%   in the homogeneous limit.  Note that the White Bear functional uses
%%   a modified form of the Carnahan equation of state.  As expected,
%%   these are all identical, and we won't include this plot in the paper
%%   (but it's here to verify that our code is working).}
%% \label{fig:free-energy}
%% \end{figure}
